%-------------------------
% Resume in Latex
% Author : Edgar
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingSpecial}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
  \textbf{\Huge \scshape Edgar Russell Teong Kai Han} \\ \vspace{1pt}
\end{center}

\begin{center}
    \small 
    \href{https://edgr.live}{\underline{www.edgr.live}} $|$ 
    \href{https://github.com/safarinexus}{\underline{github.com/safarinexus}} $|$
    \href{mailto:x@x.com}{\underline{edgargarteong@gmail.com}} $|$ 
    \href{https://linkedin.com/in/edgarteong}{\underline{linkedin.com/in/edgarteong}} $|$
    (+65) 97379450
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

  % -----------Multiple Positions Heading-----------
  %    \resumeSubSubheading
  %     {Software Engineer I}{Oct 2014 - Sep 2016}
  %     \resumeItemListStart
  %        \resumeItem{Apache Beam}
  %          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
  %     \resumeItemListEnd
  %    \resumeSubHeadingListEnd
  %-------------------------------------------
    \resumeSubheading
    {Climate Impact X}{Feb. 2025 -- Present}
    {Software Engineer}{Singapore}
    \resumeItemListStart
      \resumeItem{I Build features on the frontend and backend for CIX's main platform, a global carbon credit solutions provider jointly held by Mizuho, Standard Chartered, DBS, SGX and Temasek}
      \resumeItem{Enhance platform stability by identifying, troubleshooting, and resolving critical bugs and infrastructure issues with on both the frontend and backend}
      \resumeItem{Collaborate with QA, App Support Engineers, and Business Analysts to troubleshoot bugs and clarify feature requirements to ensure long-term platform reliability and performance}
      \resumeItem{Conducted root cause analysis and implemented preventive measures to minimize recurring issues, improving overall system efficiency}
    %  \resumeItem{Reduced server load by 62\% through asynchronous processing and thread pool management, leading to a 40\% decrease in infrastructure costs}
    %  \resumeItem{Developed and deployed new API endpoints for real-time carbon credit pricing integrated with market data providers, as well as aggregate data-fetching for both client-facing features and developer utilisations}
    %  \resumeItem{Led a team of 3 developers to build a new microservice} 
      \resumeItem{Technologies: \textbf{Java/Spring Boot, React/Vite/TypeScript, JUnit, PostgreSQL, MongoDB, Azure}}
    \resumeItemListEnd

    \resumeSubheading
    {Central Provident Fund Board (CPFB)}{Jan. 2025 -- Feb. 2025}
    {Software Engineer Intern}{Singapore}
    \resumeItemListStart
      \resumeItem{Was on the Frontier Products Team within the Business Incubator \& Accelerator Department, where I worked on docCentral, a tool that automates filling in of extensive government documents and contracts from inputs from various sources, for use across the whole of government}
      \resumeItem{Developed tools to boost team productivity, including a serverless API that auto-populates team Notion dashboard and Telegram channel from product contact form, boosting team productivity by 100\%} 
      \resumeItem{Built new features for the product, such as an admin page with a built-in dashboard, and an express product health monitoring microservice, and aided in debugging and fixing critical issues, improving product reliability and stability by 40\%}
      \resumeItem{Led the adoption of Jest unit testing on the codebase, and wrote unit tests, improving code coverage to 60\%}
      \resumeItem{Technologies: \textbf{Next.js, Node/Express, Django/Python, AWS, GitLab, MongoDB, Jest}}
    \resumeItemListEnd

    \resumeSubheading
      {Government Technology Agency (GovTech)}{Jan. 2023}
      {Software Engineer Intern}{Singapore}
      \resumeItemListStart
        \resumeItem{Worked on the Tech iOSH Refresh Project aimed at providing a more seamless portal for more than 2000 safety and health professionals, where I developed UI components, resulting in a 30\% reduction in code duplication and a 25\% increase in usability scores from user testing sessions}
        \resumeItem{Technologies: \textbf{React, Figma, HTML/CSS}}
      \resumeItemListEnd

    \resumeSubheading
      {Schneider Electric}{Aug. 2022 -- Dec. 2022}
      {Data Analyst Intern}{Singapore}
      \resumeItemListStart
        \resumeItem{Enhanced internal audit team efficiency and accuracy by leading data migration, implementing version control with GitHub, automating SQL data retrieval (reducing processing time by 30\%), and developing a machine learning algorithm for 80\% effective fraud detection}
        \resumeItem{Technologies: \textbf{SQL, Git, Python, Seaborn, Sci-kit Learn, Pandas}}
      \resumeItemListEnd

      \resumeSubheading
      {Accenture}{June. 2022 -- Aug. 2022}
      {Summer Analyst (Technology)}{Singapore}
      \resumeItemListStart
        \resumeItem{Developed testing tools and performed UAT Testing for iHiS Billing Transform project, aimed at digitally transforming the nationwide healthcare billing solution, where I used Python and SOAP APIs to test the platform and develop testing tools and scripts. I identified over 60 critical defects and reduced post-release issues by 30\%}
        \resumeItem{Technologies: \textbf{Python, SOAP APIs}}
      \resumeItemListEnd

      \resumeSubheading
      {EY}{Dec. 2021 -- Feb. 2022}
      {Audit \& Assurance Intern}{Singapore}

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
        {\textbf{\href{https://edgr.live}{Portfolio Website}} $|$ \emph{Next.js, React.js, TypeScript, TailwindCSS, GSAP, Vercel, MDX}}{Oct. 2024}
          \resumeItemListStart
          \resumeItem{My own personal portfolio website made from scratch, showcasing my personality, projects and experience.}
          \resumeItem{Built and designed entirely by me.}
          \resumeItemListEnd
      \resumeProjectHeading
        {\textbf{\href{https://edgr-odin-blog-access.vercel.app/}{Blog API}} $|$ \emph{Node, React, TailwindCSS, PostgreSQL + Prisma, Railway, Vercel, Supabase}}{Aug. 2024}
          \resumeItemListStart
            \resumeItem{Personal project of a Blog API with admin and viewer frontends, made from scratch.}
            \resumeItem{User authentication with JSON Web Tokens, as well as full stack deployment using Railway for the backend and Vercel for frontends}
          \resumeItemListEnd
        \resumeProjectHeading
        {\textbf{\href{https://safarinexus.github.io/edgr-odinprojects/}{TOP Projects}} $|$ \emph{React, PostgreSQL, Prisma, Node.js, Express.js, Webpack, REST API}}{Feb. 2024 -- Sept. 2024}
          \resumeItemListStart
          \resumeItem{A collection full-stack projects developed in my undertaking of "The Odin Project" where I self-taught full-stack development}
          \resumeItem{Projects include frontend webs app such as a weather app and React shopping page, and full-stack web apps such as an inventory site and a RESTful blog API. All built from scratch.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills and Interests}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      {Languages}{: \textbf{TypeScript/JavaScript}, \textbf{Node.js}, \textbf{Python}, \textbf{Java}, \textbf{Go}, \textbf{SQL (PostgreSQL + Prisma)}, C/C++, HTML/CSS, R, PHP} \\
      {Frameworks}{: \textbf{Next.js/React.js}, \textbf{Express.js}, \textbf{Spring Boot}, \textbf{TailwindCSS}, Jest/Vitest, JUnit, GSAP Animation Library} \\
      {Developer Tools}{: \textbf{Git/GitHub/GitLab}, \textbf{AWS}, \textbf{Azure}, \textbf{Webpack}, \textbf{MongoDB}, \textbf{Docker}, Supabase, Vercel, Figma} \\
      {Libraries}{: pandas, NumPy, Matplotlib, seaborn, sci-kit learn} \\
      {Interests}{: I’m a computer nerd, I’m a coffee nerd, I’m a mechanical keyboard nerd, I’m a book nerd, I’m a film nerd}
    }}
 \end{itemize}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Singapore Management University}{Aug. 2020 -- Dec. 2024}
      {Bachelor of Accountancy with Second Major in Computer Science}{Singapore}
      \resumeItemListStart
        \resumeItem{\textbf {Relevant Coursework:} Web App Development, Computational Thinking (Data Structures \& Algorithms), Software Engineering, Data Management}
        \resumeItem{\textbf {Semester Abroad/Exchange:} University of St. Gallen, Switzerland (Fall 2023)}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
